Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-12-13 main.tex
:pencil: Link abbreviations

\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}

@@

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary Quadrature Amplitude Modulation (QAM) at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary Phase Shift Keying (PSK) with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}

			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-PSK corresponds to ideal Intelligent Reflecting Surface (IRS) with $M$ discrete states.
			\end{remark}
		\end{subsection}
	\end{section}

	\begin{section}{Backscatter Detection and Achievable Rates}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard CSCG distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-PSK modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the AP, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent Additive White Gaussian Noise (AWGN) at block $n$. Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_primary_channel}
			\end{equation}

			\begin{remark}
				The proposed symbiotic radio system includes a multiplicative Multiple Access Channel (MAC) where the AP and the tags simultaneously transmit to the user. It inspired [TODO] to perform Successive Interference Cancellation (SIC) that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages. This scheme requires non-coherent coding at the AP and $K$ re-encoding, precoding, and subtraction operations at the user. However, different from the conventional MAC with Superposition Coding (SC), the symbiotic radio system involves Multiplication Coding (MC) that combines the primary and secondary messages by multiplication. Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent Ambient Backscatter Communications (AmBC) detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the AP, and can be readily implemented over legacy downlink systems.

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by SIC.
			\end{remark}

			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$. For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			\begin{remark}
				The backscatter links essentially form a discrete-input continuous-output memoryless channel. To further reduce decoding complexity, we apply hard-decision detection and construct a Discrete Memoryless Thresholding Channel (DMTC), whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
			\end{remark}

@@

			Consider the Maximum-Likelihood (ML) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{ML}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{ML}},
				\label{eq:decision_rule}
			\end{equation}
			and the detection threshold is
			\begin{equation}
				T_{i,{i'}}^{\mathrm{ML}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
				\label{eq:detection_threshold}
			\end{equation}

			\begin{remark}
				Although the ML decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag BIBO case.
			\end{remark}

			Once the decision region is determined, we can formulate an equivalent point-to-point DMC from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$. The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Merge with precoder design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with the CSI knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless MAC by \eqref{eq:mac}.
		\end{subsection}

@@

			Evidently, for a given discrete memoryless MAC with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless MAC.}
		\end{subsection}

@@

			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a Block Coordinate Descent (BCD) method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless MAC can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\mathcal{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless MAC (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless MAC, the capacity can be achieved by an elementary discrete memoryless MAC included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless MACs.}

			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity. The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary MAC (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions. Also, the capacity of an arbitrary MAC is achieved by an elementary MAC included within.}
			% We restrict the discussion of this paper to elementary MACs.

>>>>

\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

@@

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary \gls{qam} at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary \gls{psk} with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}

			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-\gls{psk} corresponds to ideal \gls{irs} with $M$ discrete states.
			\end{remark}
		\end{subsection}
	\end{section}

	\begin{section}{Backscatter Detection and Achievable Rates}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems. In the primary downlink system, the \gls{ap} transmits information to the single-antenna user. In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user serves as the multi-tag backscatter reader. Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging. One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard \gls{cscg} distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-\gls{psk} modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the \gls{ap}, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent \gls{awgn} at block $n$. Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_primary_channel}
			\end{equation}

			\begin{remark}
				The proposed symbiotic radio system includes a multiplicative \gls{mac} where the \gls{ap} and the tags simultaneously transmit to the user. It inspired [TODO] to perform \gls{sic} that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages. This scheme requires non-coherent coding at the \gls{ap} and $K$ re-encoding, precoding, and subtraction operations at the user. However, different from the conventional \gls{mac} with \gls{sc}, the symbiotic radio system involves \gls{mc} that combines the primary and secondary messages by multiplication. Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent \gls{ambc} detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the \gls{ap}, and can be readily implemented over legacy downlink systems.

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by \gls{sic}.
			\end{remark}

			To explicitly specify the instances of the backscatter symbols, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \in \mathcal{M} : k \in \mathcal{K}\}$ and label the corresponding tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} \in \mathcal{C} : m_k \in \mathcal{M}, k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and \gls{awgn} $w[n]$, and thus follows \gls{cscg} distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$, where the variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(\bar{c}_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			denotes the expectation of the received power per primary block under tag modulation index set $m_{\mathcal{K}}$. For the ease of exposition, we denote the hypothesis that the tag input combination at status $i \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$ as $\mathcal{H}_i$, sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order by a one-to-one mapping $m_{\mathcal{K}} \mapsto i$,\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} define the received signal energy over $N$ primary blocks as $z \triangleq \lVert \boldsymbol{y} \rVert^2$, and let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Correspondingly, $z$ is the sum of $N$ i.i.d. exponential variables each with mean $\sigma_i^2$, and the conditional probability density function follows Erlang distribution with shape $N$ and scale $\sigma_i^2$ as
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} (N-1)!}.
				\label{eq:energy_distribution}
			\end{equation}

			\begin{remark}
				The backscatter links essentially form a discrete-input continuous-output memoryless channel. To further reduce decoding complexity, we apply hard-decision detection and construct a \gls{dmtc}, whose capacity is a function of both input distribution and decision thresholds \cite{Nguyen2018}.
			\end{remark}

@@

			Consider the (\gls{ml}) detector for example. The likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_{i'}$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) = \frac{f(z \mid \mathcal{H}_i)}{f(z \mid \mathcal{H}_{i'})} = \left( \frac{\sigma_{i'}^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_{i'}^2}{\sigma_i^2 \sigma_{i'}^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			the corresponding decision rule is
			\begin{equation}
				\Lambda_{i,{i'}}^{\mathrm{\gls{ml}}}(z) \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_{i'}}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,{i'}}^{\mathrm{\gls{ml}}},
				\label{eq:decision_rule}
			\end{equation}
			and the detection threshold is
			\begin{equation}
				T_{i,{i'}}^{\mathrm{\gls{ml}}} \triangleq N \frac{\sigma_i^2 \sigma_{i'}^2}{\sigma_i^2 - \sigma_{i'}^2} \log \frac{\sigma_i^2}{\sigma_{i'}^2}.
				\label{eq:detection_threshold}
			\end{equation}

			\begin{remark}
				Although the \gls{ml} decision threshold is optimal in terms of the likelihood function, it is not necessarily capacity-achieving, although the performance gap can be negligible in the single-tag \gls{bibo} case.
			\end{remark}

			Once the decision region is determined, we can formulate an equivalent point-to-point \gls{dmc} from tag input combination alphabet $\mathcal{M^K}$ to output energy level alphabet $\mathcal{M^K}$. The probability of receiving energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Merge with precoder design.}
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:point_to_point_channel}
			\end{equation}

			On top of this, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless \gls{mac}. The probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(\bar{z}_j \mid \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus \{k\}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(\bar{z}_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, with the \gls{csi} knowledge and for any given precoder and detection threshold set, we can obtain the expected power of the received signal per block by \eqref{eq:receive_variance}, the conditional probability density function of the accumulated energy by \eqref{eq:energy_distribution}, the decision region by \eqref{eq:decision_region}, the equivalent point-to-point channel by \eqref{eq:point_to_point_channel}, and the discrete memoryless \gls{mac} by \eqref{eq:mac}.
		\end{subsection}

@@

			Evidently, for a given discrete memoryless \gls{mac} with transition probability $P(z \mid c_{\mathcal{K}})$, the information function $I_{\mathrm{B}}(\bar{c}_{m_{\mathcal{K}}} ; z)$ and mutual information $I_{\mathrm{B}}(c_{\mathcal{K}} ; z)$ only depend on the tag input distribution $\mathcal{P}$.\footnote{Note that the contribution of the precoder and detection threshold are modelled within the discrete memoryless \gls{mac}.}
		\end{subsection}

@@

			As problem \eqref{op:rate_region} is not jointly convex over $\mathcal{P}$, $\mathcal{T}$ and $\boldsymbol{w}$, we propose a \gls{bcd} method that iteratively updates the input distribution, decision region, and transmit precoder, until convergence is achieved.
		\end{subsection}

		\begin{subsection}{Input probability distribution}
			For any fixed decision boundary $\mathcal{T}$ and transmit precoder $\boldsymbol{w}$, the equivalent discrete memoryless \gls{mac} can be determined by \eqref{eq:mac}, and problem~\eqref{op:rate_region} boils down to
			\begin{maxi!}
				{\scriptstyle{\mathcal{P}}}{I}{\label{op:input_probability_distribution}}{}
				\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
			\end{maxi!}
			which is non-convex for $K > 1$ due to the product term $\prod_{k \in \mathcal{K}} P_k(\bar{c}_{m_k})$. Fortunately, the \gls{kkt} conditions are sufficient and necessary for this type of problem, and the proof follows straightforwardly from \cite{Watanabe2009}.\footnote{For any elementary discrete memoryless \gls{mac} (sizes of input alphabets are no greater than that of output alphabet), the sufficiency can be proved by combining the local maximum and connectedness of \gls{kkt} solutions. For any general discrete memoryless \gls{mac}, the capacity can be achieved by an elementary discrete memoryless \gls{mac} included within. Thus, we restrict the discussion of this paper to elementary discrete memoryless \gls{mac}s.}

			% Although the domain is non-convex for $K>1$, the \gls{kkt} conditions are sufficient and necessary for an input distribution to achieve the weighted sum-capacity. The proof follows straightforwardly from \cite{Watanabe2009} and details are omitted here.\footnote{For any elementary \gls{mac} (the sizes of input alphabets are no greater than that of the output alphabet), the sufficiency can be proved by local maximum and connectedness of \gls{kkt} solutions. Also, the capacity of an arbitrary \gls{mac} is achieved by an elementary \gls{mac} included within.}
			% We restrict the discussion of this paper to elementary \gls{mac}s.
